Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
The samples are done. Need to fit models.

pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))

@@

@@

```{r fig.width=8}
# SAMPLING --------------------------------------------------------------

samp.size <- 50000
all.samples <- rep(0,samp.size)
categ <- rep(0,samp.size)

for(i in 1:samp.size){

  which.cat <- sample(1:4, size=1, replace=TRUE, prob=pis)
  all.samples[i] <- rlnorm(n=1,meanlog=pars$mu[which.cat], sdlog=pars$sigsq[which.cat])
  categ[i] <- which.cat
}

## PLOT the samples ---------------------------------------------
# This is our f(x) from the main text
data.tail <- data.frame(values = all.samples, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)
#head(data.tail)

ggplot(data.frame(all.samples), aes(x = all.samples)) +
  geom_histogram(bins = 100) +
  geom_point(data = data.tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_minimal() -> sampleshist

ggplot(data.frame(all.samples), aes(x = all.samples)) +
  geom_density() +
  labs(y = "Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_minimal() -> samplesdens

Testing the results if using purrr instead of a for loop:

```{r fig.width=8}
#Trying an alternative way of drawing the samples

cat.samp.sizes <- samp.size*pis

@@

@@

@@

```{r echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds

>>>>

pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 250))

@@

# ### PLOT the mixture components CDF -------------------------------
# lnorm_cdfs <- purrr::map(1:4, function(y) stat_function(fun = plnorm,
#                                                              args = list(meanlog = pars$mu[y], sdlog = pars$sigsq[y]),
#                                                              color = dens_cols[y], size=1))
# ggplot() +
#   lnorm_cdfs +
#   theme_minimal() +
#   labs(y = "Density") +
#   lims(x = c(50, 250), y = c(0.9, 1))
#        
```

@@

```{r fig.width=8}
# Using purrr to get samples instead of a for loop. More efficient.
samp.size <- 50000
cat.samp.sizes <- samp.size*pis

@@

data.tail <- data.frame(values = simplsamps$data, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)

@@

Answering some questions about the underlying process.

What is the true CDF of the function that generates the process? This is the CDF of the mixture distribution, which is straightforward to calculate.

$$
f(x) = \sum_{i=1}^n w_i p_i(x) \Rightarrow F(x) = \sum_{i=1}^n w_i P_i(x)
$$

```{r}
thresh.vals <- c(100, 250, 500, 750, 1000)
samp.sizes <- c(80, 200, 500, 800, 1000, 1600)

The thresholds we want to consider are the following:`r thresh.vals` and the weights haven't changed. So, we get the cdf for each $p_i(x)$ for each threshold. This means we get $P(x >= c(100, 250, 500, 1000))$ for each curve and weigh it.

```{r eval = FALSE}
# Getting weird stuff so taking this step by step
y <- 4

ggplot() +
  stat_function(fun = dlnorm, args = list(meanlog = pars$mu[y], sdlog = pars$sigsq[y]),
                                                             color = dens_cols[y], size=1) +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150), y = c(0,0.05))

cdfs <- NULL
for(y in 1:4){
  a <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE)
  b <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE) * pis[y]

  c <- rbind(a,b)

  out <- cbind(c, c(y, y))

  cdfs <- rbind.data.frame(cdfs, out)
}
names(cdfs) <- c(thresh.vals, "curve")
cdfs

```{r}
weighted.cdfs <- NULL
for(y in 1:4){
  a <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE) * pis[y]
  weighted.cdfs <- rbind(weighted.cdfs, a)
}
w.cdfs <- colSums(weighted.cdfs)

tibble(thresh.vals) %>% 
  mutate(w.cdfs = w.cdfs,
         w.cdfs = round(w.cdfs, 5),
         samp.n = map_dbl(1:length(thresh.vals), function(y) length(which(simplsamps$data >= thresh.vals[y]))),
         samp.p = signif(samp.n/samp.size, 3)) %>% 
  knitr::kable()

@@

```{r eval = FALSE, echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds
